Stellar Bars in Isolated Gas-Rich Spiral Galaxies Do Not Slow Down

### 2023-04-21 paper/ms.tex
Expand on discussion of previous literature

>>>>

\subsection{Previous Simulation Work}
Substantial work has been devoted to the role of gas in bar dynamics.

To our knowledge the first work on a barred galaxy with a gas component was by
\citet{1993AA...268...65F}. They found a stable pattern speed when a dissipative
component was added to the system, with a slight increase in the pattern speed
near the end of their simulation. However, their model was only evolved for
$\sim1\,\textrm{Gyr}$, so it is unclear if their bar exhibits a stable pattern
speed over several Gyr.

\citet{2007ApJ...666..189B} describe a model containing up to $8\%$ gas. Their
disk is similar to ours (though their dark matter halo is a factor of $10$ less
massive). They find slowdown behavior up to a gas fraction of $8\%$, with the
finding that higher gas fractions lead to a reduced slowdown. However, for the
models which they show pattern speeds they do not include star formation or the
removal of gas from the center of their disk. In preliminary work, we found
slowdown behavior in an adiabatic model with similar gas fractions but lacking
any method for removing gas from the central region (in our fiducial SMUGGLE
model this is achieved through star formation). We surmise that the removal of
gas from the central region is an important requisite for stable pattern speeds,
though a careful torque analysis is necessary to be sure.

\citet{2010ApJ...719.1470V} do find stable pattern speeds in models with gas
fractions as low as $8\%$ (depending on the force softening used). Crucially,
their model does contain a routine for removing gas from the central region of
the disk. These authors state the behavior is bimodal, with a clear stable
regime and a slowdown regime. These authors make no mention of the process by
which the halo braking process is arrested, as we propose in the present paper.

\citet{2013MNRAS.429.1949A, 2014MNRAS.438L..81A} find stable evolution in \Rot{}
for a triaxial halo over $10\,\textrm{Gyr}$ with initial (final) gas fractions
of $100\%$ ($7\%$), $75\%$ ($6\%$), and $50\%$ ($5\%$). For a model with $20\%$
($3\%$) gas fraction they find an increasing \Rot{}. In their model with a
spherical halo they always find increasing \Rot{}, contrary to the present work. We note there is a structural difference in the dark matter halo compared to the present work. They use a cored isothermal sphere as opposed to our Hernquist halo -- it is not clear to us the impact this would have on the expected These authors make no
mention of the process by which the halo braking process is arrested, as we
propose in the present paper.

\citet{2015MNRAS.454.3166A} describe a model containing gas and stars which
slows down with time. In their model gas is added to the system to target a gas
fraction of $10\%$. However, their disk is about a factor of $10$ less massive
than the disk considered in this work. The necessary gas fraction for a stable
pattern speed probably depends on galaxy properties like mass. It is unclear
whether $10\%$ is sufficient for their bar to have a stable pattern speed.
